A holomorphic approach to membranes and fivebranes

### 2022-07-06 fivebranes/twisted.tex
merge

\documentclass[11pt]{amsart}%

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}
\newcommand{\thfd}{\Bar{D}}
\newcommand{\thfdel}{D}

\begin{document}

\section{Twisted eleven-dimensional supergravity}
%
\subsection{A model for minimally twisted supergravity}

@@

In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze `twisted $M$ theory'. 
This theory is obtained from \brian{finish}

@@

\subsection{Twisted Backreactions}

@@

Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
\[
\alpha = f(w) \delta^{(r)}_{z=0} 
\]
where $f$ is some holomorphic function. 
Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
\[
\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
\]

@@

\brian{finish}

>>>>

%\documentclass[11pt]{amsart}%
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%
%\begin{document}
%

\newcommand{\thfd}{\Bar{D}}
\newcommand{\thfdel}{D}

\section{Twisted eleven-dimensional supergravity}

\subsection{A model for minimally twisted supergravity}

@@

In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze twists of $M$ theory, starting with an $\Omega$-deformation of the nonminimal twist of eleven-dimensional supergravity. Using a type IIA description, the theory was shown to admit a description in terms of a holomorphic-topological gauge theory in five dimensions with a well-behaved quantization.

The five-dimensional theory is also a $\Z/2$-graded within the BV formalism and exists on any manifold of the form
\[
  S\times Y
\]

where $Y$ is a holomorphic-symplectic surface and $S$ is a real oriented smooth one-dimensional manifold.

The fields of the theory are given by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
\beqn
\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
\eeq.

The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket. This can be extended in a graded way to the entire Dolbeault complex; \cL_{5d} is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
The five-dimensional theory

@@

\subsection{States in twisted supergravity}

@@

Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
\[
\alpha = f(w) \delta^{(r)}_{z=0} 
\]
where $f$ is some holomorphic function. 
Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
\[
\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
\]
Linear combinations of such states form a dense subspace of all possible modifications at the boundary.

@@
